Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
trivial

\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
machine is similar to \ineffCEK{}. 
The most important differences are in values and continuations.
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values injected to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

>>>>

\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
machine is similar to \ineffCEK{}. 
The most important differences are in values and continuations.
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values casted to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.
